---
title: "Data Carpentry Example"
author: "Erika Mudrak"
date: "June 13, 2017"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(knitr)
```

### Introduction

Markdown is a way to imbed figures and statistical outputs right into your paper or notebook, along with your written explanation of what is going on (or the entire body of your paper!). 



```{r read in data, echo=FALSE, comment=NA,warning=FALSE}

svy <- read.csv("svy_complete.csv", header=TRUE)
str(svy)
```
```{r}
library(ggplot2)  #You could have put this in the first chunk when you loaded the other libraries. 
SHplot<-ggplot(subset(svy, species_id=="SH"), aes(x=weight, y=hindfoot_length))+geom_point()
plot(SHplot)



```
```{r}
DSplot<-ggplot(subset(svy, species_id=="DS"), aes(x=weight, y=hindfoot_length))+geom_point()
plot(DSplot)
```

You can make inline code in the text part of your report.  
`this makes it look like a piece of code`

You can also calculate within the inline code by using ``r` and ` ` `

For example, the mean animal weight is `r mean(svy$weight)`, which is pretty large...  

But that is too specific.  It's better to round 
The mean animal weight is `r round(mean(svy$weight), 1)`, which is pretty large...  

###  Challenge:  Add in line text with results from the regression. 


```{r, echo=FALSE, results="hide"}
  SHmodel <- lm(hindfoot_length~ weight, data=subset(svy, species_id=="SH"))
  SHresults<-summary(SHmodel)
  SHslope <- SHresults$coefficients[2,1]
  SHpval <- SHresults$coefficients[2,4]

```
For species SH, a one gram change in weight results in a `r SHslope` cm change in hindfoot length (p=`r SHpval` and weight explains a good amount of variation (R = `r round(SHresults$r.squared, 2)`),  well... good for Ecology...

```{r, echo=FALSE}
  DSmodel <- lm(hindfoot_length~ weight, data=subset(svy, species_id=="DS"))
  DSresults<-summary(DSmodel)  
```

For species DS, weight had a significant effect on hindfoot length (F~`r DSresults$fstatistic["numdf"]`,`r DSresults$fstatistic["dendf"]`~ =`r round(DSresults$fstatistic["value"], 2)`, p=`r round(pf(q=DSresults$fstatistic["value"], df1=DSresults$fstatistic["numdf"], df2=DSresults$fstatistic["dendf"], lower.tail=FALSE), 2)`), and this model explains a good amount of variation (R = `r round(DSresults$r.squared, 2)`).


## Add in table example from kable
```{r, echo=FALSE}
avgwt <- svy %>% 
    group_by(species_id) %>%
    filter(!is.na(sex), !is.na(weight)) %>%
    summarise(meanwt  = mean(weight))
```

```{r}
kable(avgwt)
```

